karate

### 2021-11-06 inst/karate.Rmd
consistentification

```{r}
iM <- zermelo(M)
loglik(iM,karate)
loglik(karate_maxp,karate)
```

@@

```{r}
par(pty='s')
plot(log10(iM),log10(karate_maxp),asp=1,xlim=c(-4,0),ylim=c(-4,0))
abline(0,1)
grid()
```

@@

```{r,label=savekaratedataset}
save(karate_table,karate,karate_maxp,file="karate.rda")
```

>>>>

```{r}
karate_zermelo <- zermelo(M)
loglik(karate_zermelo,karate)
loglik(karate_maxp,karate)
```

@@

```{r}
par(pty='s')
plot(log10(karate_zermelo),log10(karate_maxp),asp=1,xlim=c(-4,0),ylim=c(-4,0))
abline(0,1)
grid()
```

@@

```{r,label=savekaratedataset}
save(karate_table,karate,karate_maxp,karate_zermelo,file="karate.rda")
```
